---
title: "An Introduction to R - Used Car Prices"
author: "Lukas Vogt, Philipp Thienel"
date: "28 November 2015"
output: pdf_document
---

\pagebreak

# Table of content

### 1. The problem
### 2. Reproducing the analysis
#### 2.1 Structure of the documents
#### 2.2 Dependencies & required libraries
### 3. The dataset
#### 3.1 Reading the data
#### 3.2 Cleaning the data
#### 3.3 Adding features to data
### 4. Explorative analysis
### 5. Fitting a linear model
### 6. Evaluation of fit and predictive power

\pagebreak

# 1. The problem
The following problem was given:

The dataset contains records of a website selling used cars from Jul 2011. Along with the price you find various characteristics of different VW station wagons (Golf, Passat, Bora, Caddy, Multivan).

1. Import data and clean it appropriately
2. Analyze the dataset from a descriptive point of view. What do you observe for prices? How have they potentially been sampled?
3. Find a regression model that has the prices as dependent variable. Look at different models and try to identify variable that you expect to drive the price. Also think about dummies and interaction terms. Construct an additional variable “age”, i.e., the difference between the first registration (inverkehrssetzung) of the vehicle and Jul 2011.
4. Which is the most reasonable / best regression model? Does it explain the prices well?
5. Illustrate your findings graphically as well as in tabular and text form.

# 2. Reproducing the analysis
To reproduce the analysis the reader can just execute all steps as shown by himself using the datasets, scripts and functions that can be found under the following url 'https://github.com/philippthienel/hsg-intro-r-a03'.

The user is advised to download the full repository, set the working directory to the parent folder, and execute the scripts from there.

## 2.1 Structure of the documents
The repository under this url contains two folders, several R scripts and two markwdown documents.

The data folder contains the dataset that will be used in this analysis under the name 'vw_station_wagons.csv'

The R scripts containing all code used in this analysis are:

* A03_read_clean.R -
* A03_descriptive.R - 
* A03_explorative.R - 
* A03_simulation.R -

## 2.2 Dependencies & required libraries
Following R libraries will be required to run the analysis:

* ggplot2
* knitr
* stringr
* reshape2

```{r include=FALSE}
library(ggplot2)
library(knitr)
library(stringr)
library(reshape2)
```


# 3. The dataset
The dataset can be downloaded here: 'https://github.com/philippthienel/hsg-intro-r-a03'.
According to the problem the dataset "contains records of a website selling used cars from Jul 2011". The dataset of interest is 'vw_station_wagon.csv'. The file 'variables.csv' provides a list of all variable names in the dataset along with english explanations.

```{r}
variable.names <- data <- read.csv("./data/variables.csv", sep=';')
kable(variable.names)
```


## 3.1 Reading and the data
The dataset is contained in the folder 'data'. The file 'A03_read_clean.R' contains all code to read and prepare the data for the analysis.

We will read the dataset and assign the dataframe to 'data':
```{r}
path.data <- './data/vw_station_wagons.csv'
data <- read.csv(path.data, sep=',')
```

## 3.2 Cleaning the data
We can easily see that the dataset is not in a perfect condition for further analysis, particularly with regards to two points:

1. Some variables include units in the datafield and are encoded as character, while they should be integer or numeric
2. Some variables are encoded as integer but should rather be treated as factor



**1. Removing the units**

The variables 'kilometer', 'verbrauch', 'leergewicht' 'co2.emission', 'garantie' and 'preis' all include their respective units in the datafield. Naturally the variables are therefor encoded as 'character' or 'factor'. This makes mathematical calculations and transformationson those variables impossible and we have to remove the units and cast those variables as 'numeric'.

```{r}
index <- c('kilometer', 'verbrauch', 'leergewicht', 'co2.emission', 'garantie', 'preis')
kable(head(data[,index]))
```


To remove the units from the data we will define a function that takes a character vector as input, extracts the first numerical sequence in every element of the input vector and returns these tuples in a numerical output vector of the same length as the input.

```{r}
GetValue <- function(x) {
  require(stringr)
  x <- gsub("'","",x)
  x <- str_extract(x, '[0-9]+\\.*[0-9]*')
  return(as.numeric(x))
}
```

Then we will call this function on all variables of the dataset, that included units, replacing the old values.
```{r}
data <- within(data,{
  kilometer <- GetValue(kilometer)
  leergewicht <- GetValue(leergewicht)
  verbrauch <- GetValue(verbrauch)
  co2.emission <- GetValue(co2.emission)
  garantie <- GetValue(garantie)
  preis <- GetValue(preis)
})
```

As we can see, the variables are now numerical and do not include the units any longer.
```{r}
index <- c('kilometer', 'verbrauch', 'leergewicht', 'co2.emission', 'garantie', 'preis')
kable(head(data[,index]))
```

**2. Convert integer variables to factors**

The variables 'tueren', 'sitze' and 'zylinder' are encoded as integer. They take on only a few values and are better interpreted as factors. So we will want to convert them.
```{r}
kable(sapply(data[,c("tueren","sitze","zylinder")], class))
```

To convert them we can simply cast the respective variables as factors.
```{r}
data <- within(data,{
  tueren <- as.factor(tueren)
  sitze <- as.factor(sitze)
  zylinder <- as.factor(zylinder)
})
```


## 3.3 Adding features to the data
Apart from the variables that are explicitly provided in the dataset, there are further variables that can be useful for the regression modeling later on.

Three additional features that can easily be extracted from the existing variables:

1. plattform of the model (Golf, Bora, Passat etc.) - can be extracted from the 'modell' variable
2. age of the car in months - we will just take the time difference between first registration and July 2011 (when the data was sampled) as an approximation 
3. displacement in litres - can be optained by dividing 'hubrauminccm' by 1000

**1. Extracting the 'plattform' from the 'model' variable.**

The plattform is always the second word in the 'modell' variable. So we need to extract only the second word of every element of that variable. 

Noting that the first word is always 'VW', we can define a function 'GetPlattform' that takes a character vector as input, removes any string 'VW' from every element, and then extracts always the first character sequence of length >= 1 until the first character that is not a letter.

```{r}
GetPlattform <- function(x) {
  require(stringr)
  x <- gsub('VW','',x)
  plattform <- str_extract(x, '[a-zA-Z]+')
  return(plattform)
}
```

We call this function on the variable 'modell' to extract the plattform and assign it to the variable 'plattform'
```{r}
data$plattform <- as.factor(GetPlattform(data$modell))
```

**2. Calculating the age of the vehicle**

We can get the month and year of the first registration from the variable 'inverkehrssetzung'. This variable is of type factor and has the structure: 'month-year', so for example '01-2011'.

To calculate the age we define a function that takes a factor variable as input, splits the factor by '-' in two columns (month and year), and then calculates the difference between the month of the first registration and July 2011. 

```{r}
GetAge <- function(x, month=7, year=2011) {
  require(reshape2)
  df <- colsplit(x,"-",names=c("month","year"))
  age <- (year - df$year)*12 + (month - df$month)
  return(age)
}
```

We call that function on the 'inverkehrssetzung' variable to calculate theage of the vehicle in months and assign the values to the new variable 'age'.

```{r}
data$age <- GetAge(data$inverkehrssetzung)
```

**3. Calculating displacement in liters**

This is just the simple measure of scaling the variable 'hubrauminccm' down by factor 1000. We will keep one decimalpoint however, since it is customary to indicate the size of the engine like that.

```{r}
data$hubraum.liter <- round(data$hubraum/1000,1)
```


#4. Explorative analysis
All relevant code can be found in 'A03_descriptive.R' and 'A03_explorative.R'.

In the following we will conduct an explorative analysis of the variables in the dataset. This will provide important insights on which we will base the development of a linear regression model later.

The exploratorive analysis is structured as follows: 

1. Descriptive analysis of dataset
2. Dependent variable - 'preis'
3. Numeric covariates
4. Factor variables

##4.1 Descriptive analysis of dataset
First we will provide some basic facts about the dataset that we are dealing with. We are primarily interested in the following metrics:

1. Dimensions of the dataset: number of observations and variables
2. Types of variables (numeric, factors etc.)
3. Missing data - how many observations have missing values, how are they distributed

**1. Number of observations and variables**

We have a total of 1170 observations on 24 variables. Three of those variables were added by us manually ('age', 'plattform', 'hubraum.liter'). 
```{r}
dimensions <- dim(data)
names(dimensions) <- c("observations","variables")
kable(dimensions)
```

**2. Types of variables**

We can easily determine the class of every variable qnd save the result in a named vector 'variables'. For this vector the name of every element will correspond to the name of the variable.

```{r}
variables <- sapply(data, class)
```

Following variables are 'numeric' or 'integer' in the dataset.
```{r}
numerical.variables <- variables[variables %in% c("integer","numeric")]
kable(numerical.variables , col.names="class")
```

The following variables are either 'factors' or 'logical'. We will call them *categorical* to denote that they describe categories rather than numerical values (even though the categories can be numbers, like the number of doors for example). Also note that we do not have any variabls of type 'character', which is why we did not list any.
```{r}
categorical.variables <- variables[variables %in% c("factor","logical")]
kable(categorical.variables , col.names="class")
```


**3. Missing values**

Missing values are encoded as NA in the dataset. We are primirly interested in how many observations are afected by missing values overall, how those missing values are distributed over the variables (are there variables that suffer more strongly from missing values than others?), and if there is possibly a systematic component as to why values are missing.

In the whole dataset we only have 616 observations where no values are missing in any of the variables. 

```{r}
sum(complete.cases(data))
```

To display the missing values per variable we define a short function 'CountNA'. The function takes a data frame as input and returns a data frame with the numer of missing values per variable (only if count >0).

```{r}
CountNA <- function(df){
  count <- sapply(df, FUN = function(x) sum(is.na(x)))
  count <- data.frame(variable = names(count), count.na = count,
                         row.names=NULL)
  count <- count[count$count.na>0,]
  index <- order(count$count.na, decreasing=T)
  return(count[index,])
}
```


As we can see especially the variables 'energieeffizienz, 'co2.emission' and 'innenfarbe' suffer strongly from missing values.

```{r}
count.na <- CountNA(data)
kable(count.na)
```

For a graphical representation we call the function 'naBar' which is contained in the file 'naBar.R' in the functions folder. This function basically does tha same as the 'CountNA' function, but instead of a dataframe it returns a barplot (using ggplot2) counting the number of missing values per variable. For further information the reader can refer to the documentation of the function itself.

```{r}
source("./functions/naBar.R")
```

```{r}
naBar(data)
```

**Bias in missing values**

Now that we could observe a high number of missing values especially in the 'energieeffizienz' variable the question poses itself how to deal with those missing values.

Would we introduce a selection bias if we exclude the observations where the variable 'energieeffizienz' is missing?

In short: Yes, we would.

It is easy to see, that 'energieeffizienz' is missing disproportionally in lower ranges of the dependent variable 'preis'.

```{r}
plot <- ggplot(data, aes(x=preis, fill = is.na(energieeffizienz)))
plot <- plot + geom_histogram(alpha = 0.6, binwidth=1000, colour="black")
plot <- plot + scale_fill_manual(values=c("red","blue"))
plot + labs(fill = 'energieeffizien is\nmissing',
            title="Distribution of 'preis' depending on 'energieeffizienz'")
```

If we wanted to use that variable in our regression model, we would have to pay special attention on how to treat missing variables. Since we have no information on the underlying reasons for the missing values, we would have a hard time getting rid of the bias. We therefore refrain from using the that variable.

## 4.2 Dependent variable - 'preis'

In preperation for developing a regression model explaining (or predicting) the price of the cars, we will have a closer look at the 'preis' variable. 

A first look on some numerical distribution measures lead to the following observations:

* the price ranges from CHF 700 to CHF 30.000
* CHF 30.000 seems very high for a used car. We will have a look at outliers in paragraph 4.5
* median and mean are relatively close together - so that we would assume the distribution to be relatively symmetrical

```{r}
kable(t(as.matrix(summary(data$preis))))
```

A graphical representation of the distribution of 'preis' helps to substantiate some of the earlier observations. What is particularly interesting is that while the distribution seems indeed almost symmetrical, it is not concentrated around the mean or median. Instead we find a bimodal distribution. With two distinct *peaks* around CHF 5000 and CHF 25.000.

```{r}
plot <- ggplot(data, aes(x=preis))
plot <- plot + geom_histogram(binwidth=1000, fill="red", alpha=0.6, color="black")
plot
```




'Preis' strongly dependent on 'age'
```{r}
plot <- ggplot(data, aes(x=preis, y=age, colour = age)) + geom_point()
plot
```

Introducing variable 'young' (age < 60 months) and differentiate histogram by 'young'.
```{r}
# add binary variable 'young' if age < 60 months (5years)
data$young <- ifelse(data$age <60, 1, 0)

# graphical distribution differenciated by 'young'
plot <- ggplot(data, aes(x=preis, fill=as.factor(young)))
plot <- plot + geom_histogram(binwidth=1000, alpha=0.6, colour="black")
plot + scale_fill_manual(values=c("red","blue"))
```


## 4.3 Numeric covariates of interest
Interested in mainly 2 aspects:

1. Dispersion of covariates
2. Correlation between covariates

**Dispersion**
To get a better comparaility of dispersion some normalization or rescaling needed.

Decided to rescale all variables to the interval [0,1]. Where 0 is given by the minimum of the respective variable and 1 by the maximum.

Define function:
```{r}
ReScaling <- function(x){
  x.min <- min(x, na.rm = TRUE)
  x.max <- max(x, na.rm = TRUE)  
  y <- (x - x.min)/(x.max - x.min)
  return(y)
}

```

Rescale variables:
```{r}
numeric.covariates <- names(data)[sapply(data, class) %in% c("integer","numeric")]

dataScaled <- data.frame(sapply(data[,numeric.covariates],FUN=ReScaling))
```

Plot Boxplots to illustrate dispersion:
```{r, warning=FALSE, message=FALSE}
dataScaledMelt <- melt(dataScaled)
plt <- ggplot(data=dataScaledMelt, aes(x=variable, y= value))
plt + geom_boxplot(fill="red", alpha=0.6) + coord_flip()
```

**Correlation between covariates**

```{r}
# create correlation matrix
cor.matrix <- cor(data[,numeric.covariates], use="pairwise.complete.obs")
kable(cor.matrix[,1:5])
kable(cor.matrix[,6:10])
```

```{r}
source("./functions/corTiles.R")
```

```{r}
corTile(data[,numeric.covariates], use="pairwise.complete.obs")
```

## 4.4 Categorical variables

Selecting the relevant variables:
```{r}
# select relevant categorical variables (logical & factor)
categoric.variables <- c('fahrzeugart', 'aussenfarbe', 'getriebeart', 'antrieb', 'treibstoff', 'tueren', 'sitze', 'zylinder', 'plattform', 'abmfk')
kable(categoric.variables)
```

**Frequency tables**

Categorical variables that allow for easy implementation of bianry (dummy) variables:
```{r}
kable(t(as.matrix(with(data, table(getriebeart)))))
```

```{r}
kable(t(as.matrix(with(data, table(antrieb)))))
```

```{r}
kable(t(as.matrix(with(data, table(treibstoff)))))
```

```{r}
kable(t(as.matrix(with(data, table(abmfk)))))
```


Categorical variables that are multivariate:
```{r}
kable(t(as.matrix(with(data, table(aussenfarbe)))))
```

```{r}
kable(t(as.matrix(with(data, table(plattform)))))
```


# 5. Regression

## 5.1 Variable selection

We can base the decision on which variables to include in our regression on both economic reasoning and on the statistical evidence we found so far in the explorative analysis.



## 5.2 Constructing dummy variables

As we saw in the analysis of the *categorical* variables, there are mainly 4 variables that allow for an easy implemetation of dummy variables: 'getriebeart', 'treibstoff', 'antrieb' and 'abmfk'.

We will therefore implement the 4 dummies as follows:

* 'automatic' - 1: if the car has automatic gear shift (getriebeart == Automat)
* 'diesel' -  1: if the engine is a diesel (treibstoff == Diesel)
* 'by4' - 1: if the car is four wheel drive (antrieb == Allrad)
* 'abmfk' - True: if the car has 'abmfk' (is already given in dataset)

```{r}
data$automatic <- ifelse(data$getriebeart == "Automat", 1, 0)
data$diesel <- ifelse(data$treibstoff == "Diesel", 1, 0)
data$by4 <- ifelse(data$antrieb == "Allrad", 1, 0)
```

## 5.3 Fitting linear models

**1. A naive model**

```{r}
fit1 <- lm(preis ~ age + kilometer, data)
kable(summary(fit1)$coefficients)
```

**2. A linear model with level effects in age (decreasing)**

```{r}
fit2 <- lm(preis ~ sqrt(age) + kilometer ,data)
kable(summary(fit2)$coefficients)
```


**3. A linear model with level effects in age (decreasing) and dummies**

```{r}
fit3 <- lm(preis ~ sqrt(age) + kilometer + diesel + by4 + automatic , data)
kable(summary(fit3)$coefficients)
```


**4. A linear model with maximum fit (with significant coefficients)**

```{r}
fit4 <- lm(preis ~ sqrt(age) + kilometer + leistunginps + garantie + 
             leergewicht + diesel + by4 + automatic , data)
kable(summary(fit4)$coefficients)
```

## 5.4 Goodness of fit



